6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-19 paper.tex
More on the Web UI

\subsection{User Stories}
\begin{enumerate}
  \item As a developer, I would like a simple and expressive way to document my application's infrastructure requirements, so I can effectively communicate them to other developers and system administrators.
  \item As a developer, I have the ability to execute my documented infrastructure specifications to automatically validate the correctness of the system under test.
  \item As a developer, I can express arbitrary properties that the system under test must satisfy, while making use of open source libraries. So I can quickly produce accurate and practically useful specifications.
  \item As a system administrator, I can see a clear overview of the system, detailing its architecture and dependencies, so I can understand and effectively support it.
  \item As a developer / system administrator, I would like to verify the state of the system under test continuously, so I can quickly identify and resolve problems when they occur and make the system more amenable to change.
  \item As a developer / system administrator, I would like to capture changes within the system as they occur, such as code deployments or re-configuration, so I can relate these events to issues that may occur, making root cause analysis easier.
  \item As a developer / system administrator, I would like to be notified of changes in the state of the system via email and SMS, so I can respond to incidents quickly.
  \item As a system administrator, I would like to easily create specifications for applications I have already deployed.
  \item As a developer / system administrator, I would like to measure the reliability of a service and its components over time.
\end{enumerate}

\subsection{Functional Requirements}
\begin{enumerate}
  \item Testing Framework
    \begin{enumerate}
      \item The developer should be able to install the tool on their development workstation and servers.
      \item The developer should be able to use to the tool to describe a system accurately and concisely.
      \item The developer should be able to execute this description to validate the correctness of a system, verifying any arbitrary property as required.
      \item The tool should provide an auto-detection process to detect existing services and assist in describing them.
      \item The tool should provide built in checks so the developer does not have to write them all from scratch.
      \item The developer should be able to use external libraries to add additional functionality to health checks.
      \item The developer should be able to deploy this tool on a production server, and monitor the system continuously.
      \item The tool should report results back to a central location where they can be viewed.
      \item The tool should work in an environment where inbound connections to the system under test are prohibited by a firewall.
    \end{enumerate}
  \item Data Collection and Monitoring
    \begin{enumerate}
      \item The tool should effectively visualise the state of a system under test, including services, components and hosts.
      \item The tool should provide a way to view results of the health checks.
      \item The tool should provide a way to track and visualise changes happening within the system.
      \item The tool should calculate the degree of reliability of each host, service and component.
      \item The tool should send Email notifications to users when incidents occur.
      \item The tool should send SMS notifications to users when incidents occur.
      \item The data collection and monitoring should be deployable on a private network.
    \end{enumerate}
\end{enumerate}

\subsection{Non-Functional Requirements}
\begin{enumerate}
  \item Reliability - The system and all of its components should provide a reliable platform for monitoring live systems.
  \item Usability - It should be easy to start using the system and understand how it fits within the users existing organisation. Understanding of the implementation details should not be necessary for basic use cases.
  \item Performance
    \begin{enumerate}
      \item The system should efficiently validate system correctness.
      \item Alerts or warnings should be delivered in a reliable and timely fashion.
      \item Validation of the system should scale above a trivial number of hosts. (Over 20)
      \item The impact of validating correctness on the system under test should be minimal.\ i.e. no significant degradation in performance of the monitored applications or resource exhaustion of the hosts under test.
    \end{enumerate}
  \item Security - The system is intended for use in production environments, therefore it should not unnecessarily expose the target system to threats such as the following:
    \begin{enumerate}
      \item Open network ports
      \item Insecure transmission of sensitive data
      \item Remote code execution
    \end{enumerate}
  \item Maintainability - The system should be maintainable so that new features are easier to implement and the implementation is easier to understand for any open source contributors.
    \begin{enumerate}
      \item Separation of Concerns - The system should be decomposed into a number of separate components which can be built and tested in isolation. They may use different languages and frameworks as appropriate for the specific task.
      \item Architectural Patterns - The system should make good use of appropriate design patterns and architectural techniques provided in the implementation language, such as encapsulation and composition in an object orientated language.
      \item Unit Testing - Wherever possible, the code should be tested by a suite of unit tests that achieve a high coverage of the total codebase.
    \end{enumerate}
  \item Interoperability - The system should integrate with existing systems in order to provide maximum flexibility/utility to the users. It should therefore:
    \begin{enumerate}
      \item Provide a simple interface such as a HTTP API to read and write data
      \item Expose data in a standard format such as XML or JSON
    \end{enumerate}
\end{enumerate}

\subsection{Additional Aims}

@@

\subsection{Limitations}

@@

The streaming service manages the collection of check results, metrics or logs via event streams over TCP or UDP. Streams reporting errors or anomalous metrics will trigger status changes in the management API, as will streams that stop receiving messages, as this may indicate failure in the monitoring framework itself. The streaming service should be the most scalable component, as it will likely be the limiting factor in the total number of checks/hosts supported by the system.

@@

\pagebreak
\section{Web UI}
\subsection{Implementation Choices}

\subsubsection{Single Page Application}

The Web UI is implemented as a single page web application, written in JavaScript. Single page applications have recently increased significantly in popularity, due to the improved capabilities of modern browsers. A single page application differs from a traditional website in the following ways:

\begin{description}
  \item[Rendering]
    Most web applications are executed exclusively on the server-side, this is an obvious choice as it provides many benefits such as: low-latency database access, the standard execution environment of a server under the developers control and effective security. With a single page application, the server side components are usually exposed via an API which takes advantage of these benefits, and the client-side JavaScript fetches data from this API via AJAX requests. When data is received, it is rendered into HTML elements by JavaScript executing in the browser.
  \item[Interactivity and Responsiveness]
    The user experience of a single page application can be significantly better than a traditional website, when used in an appropriate situation. Websites can feel much more like a desktop application, with multiple views, background data synchronisation, data filtering etc. The main increase in responsiveness comes from eliminating jarring page reloads, thereby increasing perceived performance.
\end{description}

Abstraction and Maintainability

    Single page application frameworks often apply standard architectural patterns such as Model-View-Controller. These patterns can help to raise the level of abstraction when creating highly interactive applications beyond manually binding event listeners to DOM elements in order to update and present data. Applications that are abstracted from the imperative nature of programming with the DOM (Document Object Model) can find benefits in a more declarative approach. This can help improve testability, code reuse and can reduce the number of defects.

@@

@@

As previously discussed, Incidents are a consolidated view of relevant context that users can use to identify the root cause of issues. Users will be directed to the incident page via notifications received via Email or SMS\. The interface surfaces relevant events occurring before or during an incident, as well as similar incidents that have occurred in the past.

@@

@@

* At a glance status of all monitored services and components.
* Detailed error messages in the case of failed services, nodes or components.
* Reliability metrics calculated and augmented with Graphite stats.
* Incident tracking
* Access to the full event log

Tech
* 'Single page' application - What does this mean?
* D3.js
* SSE/WebSockets

\subsection{React.js}
\subsection{Data Visualisation - D3.js}
\subsection{Live Updates}

@@

\subsection{Non-Functional Requirements}
\begin{enumerate}
  \item Reliability - The system and all of its components should provide a reliable platform for monitoring live systems.

@@

\subsection{Critical Evaluation}

>>>>

\section{User Stories}
\begin{enumerate}
  \item As a developer, I would like a simple and expressive way to document my application's infrastructure requirements, so I can effectively communicate them to other developers and system administrators.
  \item As a developer, I have the ability to execute my documented infrastructure specifications to automatically validate the correctness of the system under test.
  \item As a developer, I can express arbitrary properties that the system under test must satisfy, while making use of open source libraries. So I can quickly produce accurate and practically useful specifications.
  \item As a system administrator, I can see a clear overview of the system, detailing its architecture and dependencies, so I can understand and effectively support it.
  \item As a developer / system administrator, I would like to verify the state of the system under test continuously, so I can quickly identify and resolve problems when they occur and make the system more amenable to change.
  \item As a developer / system administrator, I would like to capture changes within the system as they occur, such as code deployments or re-configuration, so I can relate these events to issues that may occur, making root cause analysis easier.
  \item As a developer / system administrator, I would like to be notified of changes in the state of the system via email and SMS, so I can respond to incidents quickly.
  \item As a system administrator, I would like to easily create specifications for applications I have already deployed.
  \item As a developer / system administrator, I would like to measure the reliability of a service and its components over time.
\end{enumerate}

\section{Functional Requirements}
\begin{enumerate}
  \item Testing Framework
    \begin{enumerate}
      \item The developer should be able to install the tool on their development workstation and servers.
      \item The developer should be able to use to the tool to describe a system accurately and concisely.
      \item The developer should be able to execute this description to validate the correctness of a system, verifying any arbitrary property as required.
      \item The tool should provide an auto-detection process to detect existing services and assist in describing them.
      \item The tool should provide built in checks so the developer does not have to write them all from scratch.
      \item The developer should be able to use external libraries to add additional functionality to health checks.
      \item The developer should be able to deploy this tool on a production server, and monitor the system continuously.
      \item The tool should report results back to a central location where they can be viewed.
      \item The tool should work in an environment where inbound connections to the system under test are prohibited by a firewall.
    \end{enumerate}
  \item Data Collection and Monitoring
    \begin{enumerate}
      \item The tool should effectively visualise the state of a system under test, including services, components and hosts.
      \item The tool should provide a way to view results of the health checks.
      \item The tool should provide a way to track and visualise changes happening within the system.
      \item The tool should calculate the degree of reliability of each host, service and component.
      \item The tool should send Email notifications to users when incidents occur.
      \item The tool should send SMS notifications to users when incidents occur.
      \item The data collection and monitoring should be deployable on a private network.
    \end{enumerate}
\end{enumerate}

\section{Non-Functional Requirements}
\begin{enumerate}
  \item Reliability - The system and all of its components should provide a reliable platform for monitoring live systems.
  \item Usability - It should be easy to start using the system and understand how it fits within the users existing organisation. Understanding of the implementation details should not be necessary for basic use cases.
  \item Performance
    \begin{enumerate}
      \item The system should efficiently validate system correctness.
      \item Alerts or warnings should be delivered in a reliable and timely fashion.
      \item Validation of the system should scale above a trivial number of hosts. (Over 20)
      \item The impact of validating correctness on the system under test should be minimal.\ i.e. no significant degradation in performance of the monitored applications or resource exhaustion of the hosts under test.
    \end{enumerate}
  \item Security - The system is intended for use in production environments, therefore it should not unnecessarily expose the target system to threats such as the following:
    \begin{enumerate}
      \item Open network ports
      \item Insecure transmission of sensitive data
      \item Remote code execution
    \end{enumerate}
  \item Maintainability - The system should be maintainable so that new features are easier to implement and the implementation is easier to understand for any open source contributors.
    \begin{enumerate}
      \item Separation of Concerns - The system should be decomposed into a number of separate components which can be built and tested in isolation. They may use different languages and frameworks as appropriate for the specific task.
      \item Architectural Patterns - The system should make good use of appropriate design patterns and architectural techniques provided in the implementation language, such as encapsulation and composition in an object orientated language.
      \item Unit Testing - Wherever possible, the code should be tested by a suite of unit tests that achieve a high coverage of the total codebase.
    \end{enumerate}
  \item Interoperability - The system should integrate with existing systems in order to provide maximum flexibility/utility to the users. It should therefore:
    \begin{enumerate}
      \item Provide a simple interface such as a HTTP API to read and write data
      \item Expose data in a standard format such as XML or JSON
    \end{enumerate}
\end{enumerate}

\section{Additional Aims}

@@

\section{Limitations}

@@

The streaming service manages the collection of check results, metrics or logs via event streams over TCP or UDP\@. Streams reporting errors or anomalous metrics will trigger status changes in the management API, as will streams that stop receiving messages, as this may indicate failure in the monitoring framework itself. The streaming service should be the most scalable component, as it will likely be the limiting factor in the total number of checks/hosts supported by the system.

@@

\pagebreak
\section{Web UI}

The Web UI is an important component, acting as the primary way for the user to visualize the state of the system. It provides a clear and simple interface to display services, components, events and incidents. Implementation choices and specific features are detailed further below.

\subsection{Implementation Choices}

\subsubsection{Traditional Website vs. Single Page Application}

The Web UI is implemented as a single page web application, written in JavaScript. Single page applications have recently increased significantly in popularity, due to the improved capabilities and performance of modern browsers. A single page application differs from a traditional website in the following ways:

\begin{description}
  \item[Rendering]
    Most web applications are executed exclusively on the server-side, this is an obvious choice as it provides many benefits such as: low-latency database access, the standard execution environment of a server under the developers control and improved security, eg.\ no direct database access or ability to modify the source code. With a single page application, the server side components are usually exposed via an API which takes advantage of these benefits, and the client-side JavaScript fetches data from this API via AJAX requests. When data is received, it is rendered into HTML elements by JavaScript executing in the browser.
  \item[Interactivity and Responsiveness]
    The user experience of a single page application can be significantly better than a traditional website, when used in an appropriate situation. Websites can feel much more like a native desktop application, with multiple views, background data synchronisation, data filtering etc. The main increase in responsiveness comes from eliminating page reloads, which incur the full latency penalty unless they are cached, thereby increasing perceived performance.
  \item[Deep Linking \& History]
    Browsers cater well to traditional web pages, as each page must have a uniquely accessible URL and is explicitly navigated to by clicking on a hyperlink. Single page applications must emulate this behavior using JavaScript techniques to achieve deep-linking so that bookmarks or shared URL's will navigate to the correct state within an application. Features such as the HTML5 history API enable this.
  \item[Search Engine Optimization]
    Single Page Applications are generally a poor choice where search engine rankings are important for a website. Search crawlers typically do not execute JavaScript and are therefore unable to index content effectively. For a tool such as the Monitoring UI, this is unimportant, as it is intended as an internal tool which will often be protected by a layer of authentication and not accessible from the web. Solutions for this issue are available, and involve executing the application on the server side using a JavaScript engine such as Node.js initially.
  \item[ Abstraction and Maintainability]
    Single page application frameworks often apply standard architectural patterns such as Model-View-Controller. These patterns can help to raise the level of abstraction when creating highly interactive applications beyond manually binding event listeners to DOM elements in order to update and present data. Applications that are abstracted from the imperative nature of programming with the DOM (Document Object Model) can find benefits in a more declarative approach. This can help improve testability, code reuse and can reduce the number of defects.
\end{description}

The vastly improved user experience attainable from a single page application was the primary consideration in selecting this approach. The UI is primarily read-only, but its role is to provide a near real-time view of the system from a number of different perspectives, switching between these perspectives can be seamless as a result of this implementation choice.

\subsubsection{Single Page Application Frameworks}

There are many popular Single Page Application frameworks, including: Knockout.js, Angular.js, and more recently, React.js. The frameworks vary from very small and focused (such as React.js) to the more complex and full-featured (such as Angular.js).

The Web UI is a fairly simple application, and a large framework can cause performance concerns as well as significantly increase the complexity of the code. React.js is the simplest of the mentioned frameworks, developed at Facebook and used on major sites such as Facebook, Instagram and Khan Academy, it deals with building reusable components, data binding and high performance view rendering, and its design is inspired by functional reactive programming.

React.js was chosen for this project as the simplest and most effective tool for the job, its simplicity made it extremely productive to work with.

@@

\begin{center}
  \includegraphics[scale=0.28]{web-ui/service-overview.png}
\end{center}

@@

As previously discussed, Incidents are a consolidated view of relevant context that users can use to identify the root cause of issues. Users will be directed to the incident page via notifications received via Email or SMS\@. The interface surfaces relevant events occurring before or during an incident, as well as similar incidents that have occurred in the past.

@@

\begin{center}
  \includegraphics[scale=0.28]{web-ui/incidents.png}
\end{center}

@@

\begin{center}
  \includegraphics[scale=0.28]{web-ui/events.png}
\end{center}

\subsubsection{Specification View}
The UI provides an easy way to check the exact details of a specification, by switching to its raw representation. This is intended primarily as a debugging tool.

\begin{center}
  \includegraphics[scale=0.28]{web-ui/specification.png}
\end{center}

@@

\section{Non-Functional Requirements}
\begin{enumerate}
  \item Reliability - The system and all of its components should provide a reliable platform for monitoring live systems.

@@

\section{Critical Evaluation}
